% IEEE Paper Template for US-LETTER Page Size (V1)
% Sample Conference Paper using IEEE LaTeX style file for US-LETTER pagesize.
% Copyright (C) 2006-2008 Causal Productions Pty Ltd.
% Permission is granted to distribute and revise this file provided that
% this header remains intact.
%
% REVISION HISTORY
% 20080211 changed some space characters in the title-author block
%
\documentclass[10pt,conference,letterpaper]{IEEEtran}
\usepackage{times,amsmath,epsfig}

\usepackage{subfigure}
\usepackage{color}
\usepackage{balance}  % for  \balance command ON LAST PAGE 
\usepackage{graphicx}
\usepackage{epstopdf}  % used for generating pdf 
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
% \usepackage[compress]{cite}
\usepackage[numbers,sort&compress]{natbib}
\renewcommand{\bibfont}{\footnotesize}
\usepackage{amsfonts} % for mathbb

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}


\usepackage{caption}
\usepackage{color}
\usepackage[ruled]{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmiccomment}[1]{\bgroup #1 \egroup}




\newcommand{\ie}[0]{\textit{i.e.}}
\newcommand{\eg}[0]{\textit{e.g.}}
\newcommand{\etal}[0]{\textit{et al.}}

\newcommand{\keobf}{\textit{$(k,\epsilon)$-obfuscation}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}


\theoremstyle{plain}
\newtheorem{theorem}{Theorem} 
\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}

\newcommand{\methodName}{Squid}


%
\title{Sharing Uncertain Graphs with Syntactic Anonymity}

% \author{Dongqing Xiao,  Mohamed Y. Eltabakh, Xiangnan Kong \\ 
% \affaddr{Worcester Polytechnic Institute (WPI), Computer Science Department, MA, USA} \\
% \{dxiao,~meltabakh,~xkong\}~@wpi.edu}  
\author{%
% author names are typeset in 11pt, which is the default size in the author block
{Dongqing Xiao, Mohamed Y. Eltabakh, Xiangnan Kong}%
% add some space between author names and affils
\vspace{1.4mm}\\
\fontsize{10}{10}\selectfont\itshape
Computer Science Department, Worcester Polytechnic Institute \\
Worcester, United States of America\\
\fontsize{9}{9}\selectfont\ttfamily\upshape
\{dxiao,~meltabakh,~xkong\}@wpi.edu\
}
\begin{document}
\maketitle


% NOTE keywords are not used for conference papers so do not populate them
% \begin{keywords}
% keyword-1, keyword-2, keyword-3
% \end{keywords}
%

\begin{abstract}  
Many graphs in real-world social and business applications are not deterministic, but are uncertain in nature. 
Related research requires open access to such uncertain graph datasets. While sharing these datasets often risks exposing 
sensitive user data to the public. 
However, current privacy preserving graph releasing works mainly target on deterministic graphs and overlook the uncertain scenario. 

% We first show that simply combining the representative extraction strategy and conventional graph anonymization method will result in the addition of noise that significantly disrupts uncertain graph structure. 
We first show conventional methods tailored towards deterministic graphs are not applicable. 
They significantly disrupt the structure of uncertain graph because of the disregarding the possible world semantic of uncertain graphs. 
Our work seeks a solution to release uncertain graphs with high utility without compromising user privacy. We introduce an uncertainty-aware method that provides enough privacy guarantee with much less utility loss. With the possible world semantics, it enables a fine-grained control over the injected noise. Finally, we apply our method to real uncertain graphs and show that it produces sanitized graphs that closely match the original uncertain graphs. 
% not only the statstics but also real-world applications 
\end{abstract}

\input{motivation/intro}
\input{relates.tex}
\input{notation.tex}
% \input{repOb.tex}
\input{chamelon.tex}
% \input{experiment/experiment}
% \input{conclusion.tex}
\bibliographystyle{abbrvnat}
% \bibliographystyle{abbrv}
\bibliography{refs}

\end{document}
